Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-05 causal-bandit/icml-2015/discussion.tex
Tweak

\paragraph{Cumulative Regret}
Although we have focused on simple regret in our analysis, a natural question is whether cumulative regret bounds can be obtained for the general causal bandit problem we have proposed.
% In the case of the parallel bandit problem however, we can make use of existing work on bandits with graph feedback to achieve this.

\todom{Not sure about reduction here}
Cumulative regret... use \citep{wu2015online} to get optimal cumulative regret bound (should be $\Omega(T^{2/3})$?)

General discussion of how to map parallel bandit problem to graph feedback?

@@

\paragraph{Partially or Completely Unknown Causal Graph}
A much more difficult generalisation would be to consider causal bandit problems where the causal graph is completely unknown or known to be a member of class of models.
The latter case arises naturally if we assume free access to a large observational dataset, from which the Markov equivalence class can be found via causal discovery techniques. 
Work on the problem of selecting experiments to discover the correct causal graph from within a Markov equivalence class~\cite{Eberhardt2005,eberhardt2010causal,hauser2014two,Hu2014} could potentially be incorporated into a causal bandit algorithm as part of a pre-processing step.
Simultaneously learning a completely unknown causal model while estimating the rewards of interventions would be much more challenging.
\todom{Ideas? Relevant refs?}

>>>>

\paragraph{Using the Reward Signal}

\paragraph{Cumulative Regret}
Although we have focused on simple regret in our analysis, a natural but open question is whether cumulative regret bounds can be obtained for the general causal bandit problem we have proposed.
In the case of the parallel bandit problem we can slightly modify the analysis from \citep{wu2015online} on bandits with graph feedback to get optimal cumulative regret guarantees.
Their model assumes the rewards for all arms $a$ are Gaussian with mean $\mu_a$ and variance $\sigma^2_{ab}$ and that playing an arm $a$ will reveal a side observation $Y_{ab}$ of the reward for all arms $b$ distributed with mean $\mu_b$ and variance $\sigma^2_{ab}$.
We can build a similar dependence structure with variances for a Bernoulli reward variable that is derived from the $\vec{q}$ vector of probabilities.
Even though the original results are for Gaussian rewards we believe the analysis will go through largely unchanged.

Exploiting the variance structure in this way seems necessary even in the parallel bandit case.
If instead we choose to use other graph feedback models for cumulative regret we would require those with time varying graphs~\citep{Alon2015,Kocak2014}.
Results for these models give a cumulative regret of $\bigo{\sqrt{\bar{\alpha} T}}$ where $\bar{\alpha}$ is the average independence number of the time varying graphs.
On each round, the feedback graph over the $2N$ possible interventions over $N$ binary variables would connect the chosen intervention to the corresponding intervention for each of the other $N-1$ observed variables.
Unfortunately, in this case the resulting star graphs have an $\bar{\alpha} = N$ and so the cumulative regret bounds would improve over those obtained by ignoring the causal graph structure.

@@

\paragraph{Partially or Completely Unknown Causal Graph}
A much more difficult generalisation would be to consider causal bandit problems where the causal graph is completely unknown or known to be a member of class of models.
The latter case arises naturally if we assume free access to a large observational dataset, from which the Markov equivalence class can be found via causal discovery techniques. 
Work on the problem of selecting experiments to discover the correct causal graph from within a Markov equivalence class~\cite{Eberhardt2005,eberhardt2010causal,hauser2014two,Hu2014} could potentially be incorporated into a causal bandit algorithm as part of a pre-processing step.
\todom{Ideas? Relevant refs?}
Simultaneously learning a completely unknown causal model while estimating the rewards of interventions would be much more challenging.
